Cost-effectiveness of a malaria elimination campaign

### 2017-03-10 paper.Rmd
major weather overhaul

ggplot(data = bes,
       aes(x = date,
           y = pk)) +
  geom_line(aes(color = age)) +
  facet_wrap(~district) +
  labs(x = 'Date',
       y = 'Incidence (cases per 1,000)',
       title = 'Malaria incidence over time by district',
       subtitle = 'Cases per 1,000 inhabitants') +
  scale_color_manual(name = 'Age',
                     values = c('darkgreen', 'darkorange'))
```

```{r}
x <- bes %>%
    filter(district != 'NAMAACHA') %>%
  # filter(district != 'MANHICA') %>%
  group_by(date,
           # year, month,
           # age, 
           magude) %>%
  summarise(#pk = weighted.mean(pk, w = population),
            cases = sum(cases),
            pop = sum(population),
            precip = mean(precip)) %>%
  ungroup %>%
  mutate(p = cases / pop * 1000) #%>%
  # mutate(date = as.Date(paste0(year, '-',
  #                              '06',
  #                              # month, 
  #                              '-01')))# %>%
  # filter(date >= '2014-07-01')

>>>>

ggplot(data = df,
       aes(x = date,
           y = pk)) +
  geom_line(aes(color = age)) +
  facet_wrap(~district) +
  labs(x = 'Date',
       y = 'Incidence (cases per 1,000)',
       title = 'Malaria incidence over time by district',
       subtitle = 'Cases per 1,000 inhabitants') +
  scale_color_manual(name = 'Age',
                     values = c('darkgreen', 'darkorange'))
```

```{r}
x <- df %>%
  mutate(magude = ifelse(district == 'MAGUDE', 'Magude', 'Not Magude')) %>%
    filter(district != 'NAMAACHA') %>%
  # filter(district != 'MANHICA') %>%
  group_by(date,
           # year, month,
           # age, 
           magude) %>%
  summarise(#pk = weighted.mean(pk, w = population),
            cases = sum(cases),
            pop = sum(population),
            precip = mean(precip)) %>%
  ungroup %>%
  mutate(p = cases / pop * 1000) #%>%
  # mutate(date = as.Date(paste0(year, '-',
  #                              '06',
  #                              # month, 
  #                              '-01')))# %>%
  # filter(date >= '2014-07-01')
